\bfseries Convolution-based functions on tensor fields and tensor images

### 2022-08-19 paper/main.tex
how to make all linear functions

@@

>>>>

% math macros
% HOGG SAY: I DON'T KNOW HOW TO USE AMSMATH \choose AND I'M ON A PLANE. FEEL FREE TO FIX THIS.
\renewcommand{\choose}[2]{\begin{pmatrix}{#1}\\{#2}\end{pmatrix}}

@@

SOLE: WHERE SHOULD THIS GO?
Now imagine that we want to find \emph{all} linear equivariant functions that go from an input $k$-tensor image of parity $p$ (SOLE: DO WE USE THIS CONCEPT OF PARITY PREVIOUSLY? IF NOT, IT SHOULD BE DEFINED. IT MIGHT SIMPLIFY OUR SHIT.) to an output $k'$-tensor image of parity $p'$, such that the input and output images are of the same size (both $N^d$).
Here are the linear operations (linear in the input image) that are permitted):
\begin{itemize}
\item Choose an integer $\ell$ in the range $0\leq\ell\leq k$ such that $(k'-k+2\,\ell)>0$.
  Convolve the input $k$-tensor image with a $(k'-k+2\,\ell)$-tensor invariant filter of parity $p\,p'$.
  Contract the resulting $(k'+2\,\ell)$-tensor image (of parity $p'$) with the Kroenecker delta $\ell$ times, always choosing at least one index from the indices of the input image.
  There are $$\prod_{i=1}^{\ell}\frac{1}{\ell!}\,\left[\choose{k'+2\,i}{2}-\choose{k'-k+2\,i}{2}\right]$$ possible choices for these $\ell$ Kroenecker contractions.
\item Choose an integer $\ell$ in the range $0\leq\ell\leq k-d+1$ such that $(k'-k+d-2+2\,\ell)>0$.
  Convolve the input $k$-tensor image with a $(k'-k+d-2+2\,\ell)$-tensor invariant filter of parity $-p\,p'$.
  Contract the resulting $(k'+d-2+2\,\ell)$-tensor image (of parity $-p'$) with the Levi--Civita symbol.
  There are $$\left[\choose{k'+d-2+2\,\ell}{d-1}-\choose{k'-k+d-2+2\,\ell}{d-1}\right]$$ choices for this Levi--Civita contraction.
  Then contract the resulting $(k'+2\,\ell)$-tensor image (of parity $p'$) with the Kroenecker delta $\ell$ times, always choosing one index from the indices of either the input image or of the Levi--Civita symbol.
  There are $$\prod_{i=1}^{\ell}\frac{1}{\ell!}\,\left[\choose{k'+2\,i}{2}-\choose{k'-k+2\,i}{2}\right]$$ possible choices for these $\ell$ Kroenecker contractions. (SOLE: IS THIS CONSISTENT WITH LANGUAGE ABOVE?)
\end{itemize}
